Modelling the travel time of transit vehicles in \rt through a GTFS-based road network using GPS vehicle locations

### 2019-08-04 anzjs2018/sections/02_gtfs.tex
Fix figure captions + labels

\begin{figure}[tb]
    \centering
    \begin{subfigure}{0.7\textwidth}
        \centering
        \includegraphics[width=0.95\textwidth]{figures/02_network_segments_1.pdf}
        \caption{Raw GTFS route shapes}
        \label{fig:network_creation_1}
    \end{subfigure} \\
    \begin{subfigure}{0.7\textwidth}
        \centering
        \includegraphics[width=0.95\textwidth]{figures/02_network_segments_2.pdf}
        \caption{GTFS-based road network}
        \label{fig:network_creation_2}
    \end{subfigure}
    \caption{
        Constructing a route network from the stops (dots) of three separate
        routes (lines), as shown in (a).
        Routes using the same subsequence of stops are assigned the same
        road segments, so the road network shown 
        consists of nodes (stops) and edges (roads),
        as shown in (b), where the thickness of each lines
        corresponds to how many routes share that road.
    }
    \label{fig:network_creation}
\end{figure}

>>>>

\begin{figure}[tb]
    \centering
    \begin{subfigure}{0.7\textwidth}
        \centering
        \includegraphics[width=0.95\textwidth]{figures/02_network_segments_1.pdf}
        \caption{Raw GTFS route shapes}
        \label{fig:network_creation_1}
    \end{subfigure} \\
    \begin{subfigure}{0.7\textwidth}
        \centering
        \includegraphics[width=0.95\textwidth]{figures/02_network_segments_2.pdf}
        \caption{GTFS-based road network}
        \label{fig:network_creation_2}
    \end{subfigure}
    \caption{
        Bus stops (shown as dots above) can be serviced by more than one route, 
        as shown in (a), with different line types representing three separate routes.
        The constructed road network, using stops as nodes, is shown in (b),
        in which the connecting lines represent physical road segments,
        with line width proportional to the number of individual routes 
        travelling along that road.
    }
    \label{fig:network_creation}
\end{figure}

### 2019-08-04 anzjs2018/sections/04_implementation.tex
Fix figure captions + labels

\begin{figure}[tb]
    \centering
    \includegraphics[width=0.8\textwidth]{figures/04_model_results_timing.pdf}
    \caption{
        Application timings were recorded for each component of each
        iteration, and averages over a 15~minute window are shown here.
        The timings shown are \emph{wall time}, the actual time passed,
        not CPU time.
        Steps that only involve particle calculations are approximately
        of complexity $O(N)$,
        however some steps are a little more complex (writing ETAs involves computing quantiles), 
        so there is a slightly exponential trend.
    }
        % The timings for various parts of the application, and overall. %
        % The trend is slightly non-linear due to the complexity of the ETA generation step, %
        % which requires sorting of the particle ETAs to obtain quantile estimates.}
    \label{fig:timings}
\end{figure}

>>>>

\begin{figure}[tb]
    \centering
    \includegraphics[width=0.8\textwidth]{figures/04_model_results_timing.pdf}
    \caption{
        The real-time running time of each step was recorded within each iteration,
        and the average times over a 15~minute off-peak window are shown above.
        Total time increases as the number of particles $N$ increases.
        The reason for the large contribution of writing ETAs is that
        this step involves estimation of quantiles,
        which requires sorting the particles, 
        an operation of $\mathcal{O}(N\log N)$ complexity.
        The vehicle update step also involves sorting whenever the sample
        degenerations and resampling is required.
        Total time also includes fetching the data from the API,
        which is constant for any $N$, which explains the increase
        in standardised total time for $N=500$.
    }
    \label{fig:timings}
\end{figure}
